HTW E3

### 2024-03-13 Analysis/e1.qmd
fix e3 slope computation and vx marginal effects plot

pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE1$vb), 
                     limits = c(0, 1400)) + 
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

>>>>

pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE1$vb), 
                     limits = c(0, 1400)) + 
  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

### 2024-03-13 Analysis/e2.qmd
fix e3 slope computation and vx marginal effects plot

pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE2$vb), 
                     limits = c(0, 1400)) + 
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

>>>>

pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE2$vb), 
                     limits = c(0, 1400)) + 
scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

### 2024-03-13 Analysis/e3.qmd
fix e3 slope computation and vx marginal effects plot

pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  facet_wrap(~bandOrder,ncol=1) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE3$vb), 
                     limits = c(0, 1400)) + 
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

fe <- fixef(e3_vxBMM)[,1]
fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
fixed_effect_interaction <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]

re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
  rownames_to_column("id") |> 
  left_join(e3Sbjs,by="id") |>
  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )

>>>>

pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  facet_wrap(~bandOrder,ncol=1) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE3$vb), 
                     limits = c(0, 1400)) + 
scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

fe <- fixef(e3_vxBMM)[,1]
fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]

re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
  rownames_to_column("id") |> 
  left_join(e3Sbjs,by="id") |>
  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
           fixed_effect_interaction2*(bandOrder=="Reverse") + 
           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
  slope = Estimate + adjust )
